---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# entsoeftp

The goal of entsoeftp is to give access to [one of the three](https://entsoe.zendesk.com/hc/en-us/articles/115000173266-Overview-of-data-download-options-on-Transparency-Platform) download options from the Entso-E platform. Obviously it is the FTP site, this package is for.

All dates and times are in UTC.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("krose/entsoeftp")
```
Get an access to create two variables in the .Renviron file.



## Example

There are three functions:

- list high level folders: `entsoe_list_folders()`
- list files in a folder: `entsoe_list_files()`
- download_file: `entsoe_entsoe_get_file()`

List the folders on the server:

```{r listfolders, warning=FALSE}
suppressPackageStartupMessages(library(tidyverse))
library(entsoeftp)

glimpse(entsoe_list_folders())

```


List the folders on the server:

```{r listfiles}

glimpse(entsoe_list_files(basis_name = "OutagesPU"))

```

Download af file for a specified month from the server:

```{r downloadfile}

glimpse(entsoe_get_file(basis_name = "OutagesPU"))

glimpse(entsoe_get_file(basis_name = "OutagesPU", year = 2018, month = 3))

```

